Exploring how changes in age at death and cause of death have narrowed the black-white life expectancy gap over forty-five years in the United States.

### 2017-01-05 Code/append_smoothed_results.Rmd
blach

BlackWhite$Census_Region[BlackWhite$State2 %in% c("Arizona", "Colorado", "Idaho", "Montana", 
                                                 "Nevada", "New Mexico", "Utah", "Wyoming",
                                                 "Alaska", "California", "Hawaii", "Oregon",
                                                 "Washington")] <- "West"
```

@@

>>>>

BlackWhite$Census_Region[BlackWhite$State2 %in% c("Arizona", "Colorado", "Idaho", "Montana", 
                                                 "Nevada", "New Mexico", "Utah", "Wyoming",
                                                 "Alaska", "California", "Hawaii", "Oregon",
                                                 "Washington")] <- "West"

BlackWhite$Census_Region[BlackWhite$State2 %in% c("Delaware", "Florida", "Georgia", "Maryland", 
                                                  "North Carolina", "South Carolina", 
                                                  "Virginia", "Washington DC", "West Virginia")] <- "South Atlantic"

BlackWhite$Census_Region[BlackWhite$State2 %in% c("Alabama", "Kentucky", "Mississippi", "Tennessee", 
                                                  "Arkansas", "Louisiana", "Oklahoma", "Texas")] <- "West or East South Central"

@@

cod.contributions$Census_Region[cod.contributions$State2 %in% c("Delaware", "Florida", "Georgia", "Maryland", 
                                                                "North Carolina", "South Carolina", 
                                                                "Virginia", "Washington DC", "West Virginia")] <- "South Atlantic"

cod.contributions$Census_Region[cod.contributions$State2 %in% c("Alabama", "Kentucky", "Mississippi", "Tennessee", 
                                                                "Arkansas", "Louisiana", "Oklahoma", "Texas")] <- "West or East South Central"

### 2017-01-05 Manuscript/Manuscript.Rmd
blach

#something is wrong with the percent contribution calculated for RI around 2008 ... hmmph
# ggplotly(ggplot(subset(cod.contributions, Sex2 == "Male" & Cause.of.death == "Cancers"), aes(x = Year3, y = C_x_COD_proportion)) + 
#          geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
#          ylab("Contribution to LE Gap (years)") +
#          xlab("Year") +
#          geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Male" & Cause.of.death == "Cancers"), 
#          aes(label = stabbrs), check_overlap = T, size = 2.5))
```

@@

#need to figure out what is weird about this one in NM in 2002 -- something is very odd. 
# ggplotly(ggplot(subset(cod.contributions, Sex2 == "Male" & Cause.of.death == "Cardiovascular"), aes(x = Year3, y = C_x_COD_proportion)) + 
#          geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
#          ylab("Contribution to LE Gap (years)") +
#          xlab("Year") +
#          geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Male" & Cause.of.death == "Cardiovascular"), aes(label = stabbrs), check_overlap = T, size = 2.5)
# )
```

@@

```{r figure7c, fig.align="center", fig.height=8, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod.contributions, Sex2 == "Male" & Cause.of.death == "Communicable"), aes(x = Year3, y = C_x_COD)) + 
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Male" & Cause.of.death == "Communicable"), aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

>>>>

ggplotly(ggplot(subset(cod.contributions, Sex2 == "Male" & Cause.of.death == "Cancers"), aes(x = Year3, y = C_x_COD_proportion)) +
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Male" & Cause.of.death == "Cancers"),
         aes(label = stabbrs), check_overlap = T, size = 2.5))
#the wonky percent contributions occur in the states where the LE gap crosses 0 years.

ggplotly(ggplot(subset(cod.contributions, Sex2 == "Male" & Cause.of.death == "Cancers" & C_x_COD_proportion < 0.5 & C_x_COD_proportion > -0.5), aes(x = Year3, y = C_x_COD_proportion)) +
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (%)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2000 & Sex2 == "Male" & Cause.of.death == "Cancers"),
         aes(label = stabbrs), check_overlap = T, size = 2.5))
```

@@

ggplotly(ggplot(subset(cod.contributions, Sex2 == "Male" & Cause.of.death == "Cardiovascular" & C_x_COD_proportion < 0.5 & C_x_COD_proportion > -0.5), aes(x = Year3, y = C_x_COD_proportion)) +
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (%)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2000 & Sex2 == "Male" & Cause.of.death == "Cardiovascular"),
         aes(label = stabbrs), check_overlap = T, size = 2.5))
```

@@

```{r figure7c, fig.align="center", fig.height=8, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod.contributions, Sex2 == "Male" & Cause.of.death == "Communicable"), aes(x = Year3, y = C_x_COD)) + 
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Male" & Cause.of.death == "Communicable"), aes(label = stabbrs), check_overlap = T, size = 2.5)
)

ggplotly(ggplot(subset(cod.contributions, Sex2 == "Male" & Cause.of.death == "Communicable" & C_x_COD_proportion < 0.5 & C_x_COD_proportion > -0.5), aes(x = Year3, y = C_x_COD_proportion)) +
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (%)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2000 & Sex2 == "Male" & Cause.of.death == "Communicable"),
         aes(label = stabbrs), check_overlap = T, size = 2.5))
```
